The Free-play Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-06 paper.tex
Fixed caption Fig 4
Formatting

The Free-play Sandbox provides the opportunity to observe children interacting in a natural way in an open but framed setup. As the system can run on a single computer platform it can easily be deployed in the 'wild', in places where the children naturally interact such as classroom. The quantity and thoughtfulness of information logged allows to keep a track of every interaction happening around the game.

@@

\paragraph{Child-Robot Interaction}
\label{ssec|CRI}
This Free-play Sandbox provides the opportunity to explore child-robot
interactions in this open-real world environment as shown in Figure
\ref{fig|freeplay}.

@@

With the quantity of data logged and the high number of interaction achievable with the Freeplay Sandbox, it supports the type of requirement for recent Machine Learning approaches such as deep learning. The similar position of the children in all interactions makes the combination of data from different interaction easier than other less compact systems.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{rviz-sandtray}
    \caption{The free-play sandbox, viewed at runtime within ROS RViz. The
    current background drawing (bottom left) is published on a regular image
    topic. Simple computer vision is used to segment it into zones (visible in
    the central panel). The poses and bounding boxes of the interactive items
    are published as well, and turned into an occupancy map, used to plan the
    robot's arm motion.}
    \label{fig|rviz}
\end{figure}

@@

We typically adhere to the acquisition procedure described in
Table~\ref{tab|protocal} with all participants.  To ease later identification,
each child is also given a different and brightly coloured sports bib to wear.

@@

As of today, no reliable Speech Recognition Engine exists for
children~\cite{kennedy2017child}, but in the future, the audio should provide
textual information on the requests and comments produced by the child.

@@

The coding is performed post-hoc with the help of a dedicated annotation tool
(Fig.~\ref{annotator} which is part of the Free-play sandbox toolbox. This tool
can replay and randomly seek in the three video streams, synchronised with the
recorded state of the game (including the drawings as they are created). An
interactive timeline displaying the annotations is also displayed.

@@

We have been using the free-play Sandbox task for an initial, large scale, data
collection over a period of 3 months during Spring 2017.

This campaign aimed at (1) extensively evaluating the task itself (would
children engage and exhibit a large range of social dynamics and behaviours?),
(2) making sure the whole software architecture and data acquisition pipeline
were reliable (they were), and (3) establishing two experimental baselines for
the Free-play Sandbox task: the `human' baseline on one hand (child-child
condition), an `asocial' baseline on the other hand (child - \emph{non-social}
robot condition). These two baselines are situated at the two ends of the
spectrum of social interaction. They aim at characterising the qualitative and
quantitative bounds of this social spectrum and can be used by the research
community to evaluate given interaction policies.

>>>>

The free-play sandbox provides the opportunity to observe children interacting in a natural way in an open but framed setup. As the system can run on a single computer platform it can easily be deployed in the 'wild', in places where the children naturally interact such as classroom. The quantity and thoughtfulness of information logged allows to keep a track of every interaction happening around the game.

@@

\paragraph{Child-Robot Interaction}
\label{ssec|CRI}
This free-play sandbox provides the opportunity to explore child-robot
interactions in this open-real world environment as shown in Figure
\ref{fig|freeplay}.

@@

With the quantity of data logged and the high number of interaction achievable
with the free-play sandbox, it supports the type of requirement for recent
Machine Learning approaches such as deep learning. The similar position of the
children in all interactions makes the combination of data from different
interaction easier than other less compact systems.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{rviz-sandtray}
    \caption{The free-play sandbox, viewed at runtime within ROS RViz. Simple
    computer vision is used to segment the background drawings into zones
    (visible on the right panel). The poses and bounding boxes of the
    interactive items are published as well, and turned into an occupancy map,
    used to plan the robot's arm motion.}

    \label{fig|rviz}
\end{figure}

@@

We typically adhere to the acquisition procedure described in
Table~\ref{tab|protocol} with all participants.  To ease later identification,
each child is also given a different and brightly coloured sports bib to wear.

@@

As of today, no reliable speech recognition engine exists for
children~\cite{kennedy2017child}, but in the future, the audio should provide
textual information on the requests and comments produced by the child.

@@

The coding is performed post-hoc with the help of a dedicated annotation tool
(Fig.~\ref{annotator} which is part of the free-play sandbox toolbox. This tool
can replay and randomly seek in the three video streams, synchronised with the
recorded state of the game (including the drawings as they are created). An
interactive timeline displaying the annotations is also displayed.

@@

We have been using the free-play sandbox task for an initial, large scale, data
collection over a period of 3 months during Spring 2017.

This campaign aimed at (1) extensively evaluating the task itself (would
children engage and exhibit a large range of social dynamics and behaviours?),
(2) making sure the whole software architecture and data acquisition pipeline
were reliable (they were), and (3) establishing two experimental baselines for
the free-play sandbox task: the `human' baseline on one hand (child-child
condition), an `asocial' baseline on the other hand (child - \emph{non-social}
robot condition). These two baselines are situated at the two ends of the
spectrum of social interaction. They aim at characterising the qualitative and
quantitative bounds of this social spectrum and can be used by the research
community to evaluate given interaction policies.
